The \project{UNRAVE} catalog of stellar astrophysical parameters and chemical abundances

### 2016-08-11 article/unrave.tex
foo

\title{The \project{UNRAVE} catalog}

@@

\begin{abstract}
\end{abstract}

@@

\section{Introduction} \label{sec:intro}

\acknowledgements

\begin{thebibliography}{dummy}
\end{thebibliography}

>>>>

\title{The \project{UNRAVE} catalog of stellar astrophysical parameters and chemical abundances}

@@

\begin{abstract}
% Gaia will release stuff
% Much we want to do will involve chemistry + kinematics
% RAVE has the largest overlap with Gaia DR1, but chemistry is unavailable for most stars
% We perform an independent analysis of RAVE spectra w/ The Cannon, censoring, + upgrades, to derive astrophysical parameters and detailed chemical abundances.
% We produce a catalog of up to N abundances for X stars, constituting the largest
% catalog of chemical abundances that overlap with Gaia by a factor of X.

\end{abstract}

@@

\section{Introduction} 
\label{sec:introduction}

\section{Methods}
\label{sec:methods}

\section{Validation}
\label{sec:validation}

\section{Conclusion}
\label{sec:conclusion}

\acknowledgements
% We thank,......

This research made use of: Astropy, a community-developed core Python package for
Astronomy \citep{astropy}, NASA's Astrophysics Data System Bibliographic Services;
 and \project{TOPCAT} \citep{Taylor2005}.
This work was partly supported by the European Union FP7 programme through ERC 
grant number 320360.
Funding for RAVE has been provided by: the Australian Astronomical Observatory; the Leibniz-Institut fuer Astrophysik Potsdam (AIP); the Australian National University; the Australian Research Council; the French National Research Agency; the German Research Foundation (SPP 1177 and SFB 881); the European Research Council (ERC-StG 240271 Galactica); the Istituto Nazionale di Astrofisica at Padova; The Johns Hopkins University; the National Science Foundation of the USA (AST-0908326); the W. M. Keck foundation; the Macquarie University; the Netherlands Research School for Astronomy; the Natural Sciences and Engineering Research Council of Canada; the Slovenian Research Agency; the Swiss National Science Foundation; the Science \& Technology Facilities Council of the UK; Opticon; Strasbourg Observatory; and the Universities of Groningen, Heidelberg and Sydney. The RAVE web site is at https://www.rave-survey.org.

\begin{thebibliography}{dummy}
\bibitem[Astropy Collaboration et 
al.(2013)]{astropy} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, Astronomy \& Astrophysics, 558, AA33

\bibitem[Taylor(2005)]{Taylor2005} Taylor, M.~B.\ 2005, Astronomical Data Analysis Software and Systems XIV, 347, 29

\end{thebibliography}
